---
title: "Indonesian Aquaculture Data Visualization"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


###Purpose

As part of our work towards Activity 3, we are examining the spatial patterns and trends in the Indonesian aquaculture statistics. We have prepared several visuals to give our colleagues an idea of what types of figures could be used in the technical whitepaper. Based on previous discussions, we have tried to draw attention to four provinces of interest: Banten, Jawa Barat, Jawa Timur, and Papua Barat. General thoughts and feedback are welcome. In particular, we hope to gauge how well these figures could be used to support case studies that are relevant to the grander themes and management issues of Indonesian aquaculture.

For example, some management discussions that these visuals could potentially complement include:  

* proper siting and spatial management of extensive brackish pond aquaculture  
* the regional intensification of brackish pond aquaculture and associated environmental concerns
* managing the development of low area, high intensity marine aquaculture production



```{r setup, include = F}
library(tidyverse)
library(sf)
library(viridis)
library(scales)
library(RcppRoll)

# Read shapefile
indo <- st_read(dsn = "Data/IDN_adm_shp", layer = "IDN_adm1")
# Simplify shapefile
indo <- st_simplify(indo, dTolerance = 0.01)
# Production and area data
aqua <- read_csv(file = "Data/indo_aqua_stats.csv", na = c("-"))
#Correct for Papua Barat/Irian Jaya Barat
levels(indo$NAME_1)<- c(levels(indo$NAME_1), "Papua Barat")
indo[which(indo$NAME_1 == "Irian Jaya Barat"), grep("^NAME_1$", colnames(indo))] <- "Papua Barat"
```

```{r data tidying}
# Process data into long format
aqua <- aqua %>% 
  gather(key = 'year', value = 'value', 4:ncol(.)) %>% 
  spread(metric, value) %>% 
  mutate(area_hectares = as.numeric(gsub('\\.', '', area_hectares)),
         tons          = as.numeric(gsub('\\.', '', tons)),
         tons_per_ha   = tons / area_hectares,
         NAME_1 = factor(province))
```

```{r summary stats}
# Area of brackish water ponds
area_map <- aqua %>% 
  dplyr::filter(year == 2015 & type == 'brackish pond') %>% 
  select(NAME_1, area_hectares) 

# Intensity of brackish pond production
brack_intensity_map <- aqua %>% 
  dplyr::filter(year == 2015 & type == 'brackish pond') %>% 
  select(NAME_1, tons_per_ha) %>% 
  mutate(tons_per_ha = ifelse(tons_per_ha > 1000, NA, tons_per_ha))

# Area of Marine culture
marine_area_map <- aqua %>% 
  dplyr::filter(year == 2015 & type == 'marine culture') %>% 
  select(NAME_1, area_hectares)

#Production of cage/raft aquaculture

#With NAs
prod_map <- aqua %>% 
  dplyr::filter(year == 2015 & type %in% c("cage", "floating cage net")) %>% 
  select(NAME_1, type, tons) %>% 
  group_by(NAME_1) %>% 
  summarise(tons = sum(tons))

#Without NAs

x_map <- aqua %>% 
  dplyr::filter(year == 2015 & type %in% c("cage", "floating cage net")) %>% 
  select(NAME_1, type, tons) %>% 
  group_by(NAME_1) %>% 
  summarise(tons = sum(tons, na.rm = T)) %>% 
  ungroup()

#join to spatial data

area_map <- left_join(indo, area_map)
brack_intensity_map <- left_join(indo, brack_intensity_map)
marine_area_map <- left_join(indo, marine_area_map)
prod_map <- left_join(indo, prod_map)
x_map <- left_join(indo, x_map)

```
###Visuals  
*Note: Provinces in gray either represent missing or suspect values. For example, Jawa Tengah was calculated to have an intensity above 1000 tons per hectare for brackish pond aquaculture in 2015 (two orders of magnitude higher than the next highest province).*
```{r maps}
ggplot(area_map) +
  geom_sf(aes(key = NAME_1, fill = area_hectares)) +
  scale_fill_viridis(option = "D", labels = comma, direction = -1) +
  guides(fill = guide_colorbar(barwidth = 20,
                               barheight = 0.5,
                               title = "Hectares",
                               title.position = "top")) +
  labs(title = "Area of brackish pond aquaculture in 2015") +
  theme_minimal() +
  theme(legend.position = 'bottom')
```

**Figure 1.** The extent of brackish pond aquaculture (hectares) for each province in 2015. Both Banten and Jawa Barat have relatively high amounts of area under production, with the maximum national values occurring in Kalimantan Timur and Sulawesi Tengah. 

&nbsp;



```{r}
ggplot(brack_intensity_map) +
  geom_sf(aes(fill = tons_per_ha)) +
  scale_fill_viridis(breaks = seq(from = 0, to = 40, by = 5), option = "A", direction = -1, begin = 0.2) +
  guides(fill = guide_colorbar(barwidth = 20,
                               barheight = 0.5,
                               title = "Tons per hectare",
                               title.position = "top")) +
  labs(title = "Intensity of brackish pond aquaculture in 2015") +
  theme_minimal() +
  theme(legend.position = 'bottom')

```

**Figure 2.** Provincial intensity of brackish pond aquaculture (tons/hectare) for 2015. Jawa Timur is highlighted as having more intensive production than Banten or Jawa Barat.

&nbsp;

```{r}
ggplot(marine_area_map) +
  geom_sf(aes(fill = area_hectares)) +
  scale_fill_viridis(breaks = seq(from = 0, to = 50000, by = 10000), option = "D", direction = -1) +
  guides(fill = guide_colorbar(barwidth = 20,
                               barheight = 0.5,
                               title = "Hectares",
                               title.position = "top")) +
  labs(title = "Area of marine culture production in 2015") +
  theme_minimal() +
  theme(legend.position = 'bottom')
```

**Figure 3.** The area (hectares) dedicated to marine culture production (believed to be seaweed) in 2015 for each province. Compared to brackish pond aquaculture, marine culture is also quite extensive in Sulawesi Tengah but takes up less than half the total area throughout Indonesia.  

&nbsp;

```{r}
ggplot(x_map) +
  geom_sf(aes(key = NAME_1, fill = tons)) +
  scale_fill_viridis(option = "B", labels = comma, direction = -1, begin = 0.2) +
  guides(fill = guide_colorbar(barwidth = 20,
                               barheight = 0.5,
                               title = "Tons",
                               title.position = "top")) +
  labs(title = "Production of raft/cage aquaculture in 2015") +
  theme_minimal() +
  theme(legend.position = 'bottom')
```

**Figure 4.** The amount of cage and raft aquaculture production in tons for 2015. At almost 20,000 tons, Jawa Barat produces over twice as much biomass as the next highest provinces: Sumatera Barat, Jambi, and Sumatera Utara.  

&nbsp;

####*Notes*:
During our data exploration, we encountered a few surprising results. For example, the below figure displays the area used in brackish pond aquaculture for three provinces from 2005 to 2015. All three time series demonstrate either a sharp increase or decrease in 2012. Is it possible that there is a historical explanation for this (e.g. disease outbreak)? Else, it could potentially indicate a data reporting error.


```{r, fig.height= 5, fig.width= 9}
area_plot <- aqua %>% 
  filter(province %in% c('Jawa Barat', 'Jawa Timur', 'Banten')) %>% 
  filter(type %in% c('brackish pond')) %>% 
  mutate(Province = province) %>% 
  ggplot(aes(x = as.integer(year), y = area_hectares, color = Province)) +
  geom_line()+labs(title = "Extent of brackish pond aquaculture", y = "Area (ha)", x = "Year")+scale_x_continuous(breaks = seq(2005,2015,1))+theme_classic()
area_plot
```


